---
title: "Homework 5"
author: Yuqi Wang
output: github_document
---

```{r}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


This is my solution for homework 5.

## Problem 1
read in the data

```{r}
#city_prop_test = function(df) {
#  n_unsolved ...
#  n_total ...
  
#  prop_test(n_unsolved, n_total)
#}
homicide_df = read_csv(file = "./data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition  == "Closed without arrest" ~ "unsolved",
      disposition  == "Open/No arrest" ~ "unsolved",
      disposition  == "Closed by arrest" ~ "solved",
## case_when is used to create categorical variables
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") # %>% 
  #nest(data = resolved)
```

Let's look at this a bit

```{r}
aggregate_df = homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```


Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)
  ) %>% 
  broom::tidy()
## make the test result more tidy.
```

Try to iterate...

```{r}
results_df = aggregate_df %>% 
  mutate(
    prop_test = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_test = map(.x = prop_test, ~broom::tidy(.x))
  ) %>% 
  select(-prop_test) %>% 
  unnest(tidy_test) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high))
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust =1))
```

## Problem 2 ideas

First, start with a dataframe containing the file names.
```{r}
path_df = tibble(
  path = list.files("data/lda_data")
) %>% 
  mutate(
    path = str_c("data/lda_data/", path)
  )
```

Second, import the files and tidy the longitudinal data.

```{r}
lda_df = tibble(
  id = path_df$path,
  map_df(.x = path_df$path, ~read_csv(.x))
) %>% 
  mutate(
    id = substr(id, 15, 20),
  ) %>% 
  separate(id, c("group", "id"), sep = "_", remove = TRUE) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "obs_value"
  ) %>% 
  mutate(id = as.numeric(id),
         week = as.numeric(week))
```


Third, make the plot to show observations of each subject over time.

```{r}
lda_df %>% 
  ggplot(aes(x = week, y = obs_value, group = interaction(id, group), color = group)) +
  geom_line()


interaction.plot(lda_df$week,
lda_df$id, lda_df$obs_value, xlab="time", ylab="observations", legend=F)
```

Difference between groups:

From the spaghetti plot, we found that the observed values for the control group and the experimental group were about the same at Week 1. As time went by, the observed values for people in the experimental arm was getting larger, while the values for the control group did not change. The difference in the observed value between the two groups was larger after 8 weeks' follow up.






